Adolescent well-being in the digital age

### 2022-01-20 00-models.qmd
Fit three-way interactions

```{r model1-val-bf}
#| echo: true
# Meta-regression model of outcomes
bf_1 <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex + year * age +
    (year * sex + year * age | c | country) +
    (year * sex + year * age | r | region),
  family = gaussian()
)
```

@@

```{r fit-model-2}
#| cache: false
#| results: hide
# Model formula is only a small update to Model 1
bf_2 <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex + year * age + i1_cw * sex + i1_cw * age + i1_cb +
    (year * sex + year * age + i1_cw * sex + i1_cw * age | country) +
    (year * sex + year * age + i1_cw * sex + i1_cw * age | region),
  family = gaussian()
)

@@

```{r fixed-mobile}
#| cache: false
#| results: hide
bf_2_f <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex + year * age + f1_cw * sex + f1_cw * age + f1_cb +
    (year * sex + year * age + f1_cw * sex + f1_cw * age | country) +
    (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
  family = gaussian(),
  unused = ~outcome
)

bf_2_m <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex + year * age + m1_cw * sex + m1_cw * age + m1_cb +
    (year * sex + year * age + m1_cw * sex + m1_cw * age | country) +
    (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
  family = gaussian(),
  unused = ~outcome
)

bf_2_g <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex + year * age + g1_cw * sex + g1_cw * age + g1_cb +
    (year * sex + year * age + g1_cw * sex + g1_cw * age | country) +
    (year * sex + year * age + g1_cw * sex + g1_cw * age | region),
  family = gaussian(),
  unused = ~outcome
)

>>>>

```{r model1-val-bf}
#| echo: true
# Meta-regression model of outcomes
bf_1 <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex * age +
    (year * sex * age | c | country) +
    (year * sex * age | r | region),
  family = gaussian()
)
```

@@

```{r fit-model-2}
#| cache: false
#| results: hide
# Model formula is only a small update to Model 1
bf_2 <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex * age + i1_cw * sex * age + i1_cb +
    (year * sex * age + i1_cw * sex * age | country) +
    (year * sex * age + i1_cw * sex * age | region),
  family = gaussian()
)

@@

```{r fixed-mobile}
#| cache: false
#| results: hide
bf_2_f <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex * age + i1_cw * sex * age + f1_cb +
    (year * sex * age + i1_cw * sex * age | country) +
    (year * sex * age + i1_cw * sex * age | region),
  family = gaussian(),
  unused = ~outcome
)

bf_2_m <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex * age + i1_cw * sex * age + m1_cb +
    (year * sex * age + i1_cw * sex * age | country) +
    (year * sex * age + i1_cw * sex * age | region),
  family = gaussian(),
  unused = ~outcome
)

bf_2_g <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex * age + i1_cw * sex * age + g1_cb +
    (year * sex * age + i1_cw * sex * age | country) +
    (year * sex * age + i1_cw * sex * age | region),
  family = gaussian(),
  unused = ~outcome
)
